---
title: "RDD_R"
author: "Samuel Thomas"
output: html_document
date: "2023-03-26"
---

## Documentation Links:
rddtools Documentation: http://qua.st/rddtools/docs/quick-start-guide/

Better rddtools Documentation: https://www.rdocumentation.org/packages/rddtools/versions/1.6.0

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rddtools)
library(readr)
library(ggplot2)
```

## Uploading Data

```{r}
# Reading in Data
dat <- read_csv('faps_clean.csv', show_col_types = F)
dat <- dat[,-1] # Get Rid of First Column

# Setting Columns as Factors
dat[c('adltfscat', 'fincondition','region',
      'rrindicator','targetgroup','mode_racecat_r',
      'educcat','pr_educcat')] <- lapply(dat[c('adltfscat', 'fincondition',
                                               'region','rrindicator',
                                               'targetgroup','mode_racecat_r',
                                               'educcat','pr_educcat')],
                                         as.factor)
str(dat)
```

## Log transform of Percent Poverty

```{r}
# Log Transform
dat <- dat %>% mutate(log_percent_poverty = log(percent_poverty + 1))

# Density Plot of Log Transformed Percent Poverty
ggplot(dat, aes(x = log_percent_poverty)) +
  geom_density()
```

## McCrary Test on Percent Poverty and log(Percent Poverty)

Checks that there is no manipulation around the cutoff - people manipulating their eligibility to be included or                           not included in SNAP

Note: McCrary Test is not dependent on instrument.

```{r}
# Percent Poverty

  ## Creating RDD Object
mccrary <- rdd_data(y = dat$binadltfscat, x = dat$percent_poverty,
                    cutpoint = 150,
                    covar = c(dat$region, dat$pr_age_r, I(dat$pr_age_r^2),
                                     dat$ncimmigrant_any, dat$prop_black,
                                     dat$prop_other, dat$hispanic, dat$pr_educcat, dat$nchildren,
                                     dat$nadults, dat$pr_sex, dat$disabled, dat$rural))

  ## Conducting Test
a <- dens_test(mccrary)
title(main = 'Density Estimations of Percent Poverty for McCrary Test',
      ylab = 'Density', xlab = 'Percent Poverty')

a # Better plot

# Log(Percent Poverty)

  ## Creating RDD Object
log_mccrary <- rdd_data(y = dat$binadltfscat, x = dat$log_percent_poverty,
                        cutpoint = log(150),
                        covar = c(dat$region, dat$pr_age_r, I(dat$pr_age_r^2),
                                     dat$ncimmigrant_any, dat$prop_black,
                                     dat$prop_other, dat$hispanic, dat$pr_educcat, dat$nchildren,
                                     dat$nadults, dat$pr_sex, dat$disabled, dat$rural))

  ## Conducting Test
b <- dens_test(log_mccrary)
title(main = 'Density Estimations of Percent Poverty for McCrary Test',
      ylab = 'Density', xlab = 'Percent Poverty')

b # Better plot
```

## Fuzzy RDD on Binary Food Insecurity vs log(Percent Poverty) with SNAP Eligible Instrument

```{r}
# Plot of Treatment Assignment (SNAP Eligible) vs Log(Percent Poverty)
ggplot(dat, aes(x = log_percent_poverty, y = elig_units1)) +
  geom_point() +
  geom_jitter() +
  geom_vline(xintercept = log(150), color = 'red') +
  labs(x = 'Log Percent Poverty', y = 'SNAP Eligible')


# Creating rdd data object with binadltfscat as response, log(percent_poverty) as predictor, cutpoint of log(150), and elig_units1 as instrument
log_fuzzy_rdd_bin <- rdd_data(y = dat$binadltfscat, x = dat$log_percent_poverty,
                              cutpoint = log(150), z = dat$elig_units1,
                              covar = c(dat$region, dat$pr_age_r, I(dat$pr_age_r^2),
                                     dat$ncimmigrant_any, dat$prop_black,
                                     dat$prop_other, dat$hispanic, dat$pr_educcat, dat$nchildren,
                                     dat$nadults, dat$pr_sex, dat$disabled, dat$rural))
summary(log_fuzzy_rdd_bin)

# Plot of rdd
plot(log_fuzzy_rdd_bin, nbins = 50)


# Bandwidth Calculation (Imbens-Kalyanaraman 2012)
log_bw_ik_fuzzy_bin <- rdd_bw_ik(log_fuzzy_rdd_bin)
print(log_bw_ik_fuzzy_bin)


#Nonparametric Local Linear RDD Regression
log_nonpara_fuz_bin <- rdd_reg_np(rdd_object = log_fuzzy_rdd_bin, bw = log_bw_ik_fuzzy_bin)
print(log_nonpara_fuz_bin)


#Parametric Probit RDD Regression
log_para_fuz_bin <- rdd_gen_reg(rdd_object = log_fuzzy_rdd_bin, fun = glm, bw = log_bw_ik_fuzzy_bin,
                        family = binomial(link = 'probit'),
                        slope = 'separate', order = 1)
print(log_para_fuz_bin)


# Regression Sensitivity Tests
  
  ## LATE vs bw (check sensitivity of estimate to different bandwidths)

      ### Nonparametric Fit
plotSensi(log_nonpara_fuz_bin, output = 'ggplot') + 
  xlim(log_bw_ik_fuzzy_bin - 0.1, log_bw_ik_fuzzy_bin + 0.1) +
  geom_hline(yintercept = 0, color = 'black', linetype = 'dashed') +
  labs(x = 'Bandwidth', y = 'LATE',
  title = 'Local Average Treatment Effect (LATE) vs Bandwidth') +
  theme_bw()

      ### Parametric Fit  
plotSensi(log_para_fuz_bin, output = 'ggplot') +
  xlim(log_bw_ik_fuzzy_bin - 0.1, log_bw_ik_fuzzy_bin + 0.1) +
  geom_hline(yintercept = 0, color = 'black', linetype = 'dashed') +
  labs(x = 'Bandwidth', y = 'LATE',
  title = 'Local Average Treatment Effect (LATE) vs Bandwidth') +
  theme_bw()

  ## Placebo Test (estimate RDD effect based on fake cutpoints)

      ### Nonparametric Fit
plotPlacebo(log_nonpara_fuz_bin, device = 'ggplot', output = "ggplot")

      ### Parametric Fit
plotPlacebo(log_para_fuz_bin, output = 'ggplot')
```

## Fuzzy RDD on Binary Food Insecurity vs log(Percent Poverty) with SNAP Receiver Instrument

```{r}
# Plot of Treatment Assignment (SNAP Receiver) vs Log(Percent Poverty)
ggplot(dat, aes(x = log_percent_poverty, y = snapnowhh)) +
  geom_point() +
  geom_jitter() +
  geom_vline(xintercept = log(150), color = 'red')

# Creating rdd data object with binadltfscat as response, log_percent_poverty as predictor, cutpoint of log(150), and snapnowhh as instrument
log_fuzzy_rdd_bin <- rdd_data(y = dat$binadltfscat, x = dat$log_percent_poverty,
                              cutpoint = log(150), z = dat$snapnowhh,
                              covar = c(dat$region, dat$pr_age_r, I(dat$pr_age_r^2),
                                     dat$ncimmigrant_any, dat$prop_black,
                                     dat$prop_other, dat$hispanic, dat$pr_educcat, dat$nchildren,
                                     dat$nadults, dat$pr_sex, dat$disabled, dat$rural))
summary(log_fuzzy_rdd_bin)

# Plot of rdd
plot(log_fuzzy_rdd_bin, nbins = 50)


# Bandwidth Calculation (Imbens-Kalyanaraman 2012)
log_bw_ik_fuzzy_bin <- rdd_bw_ik(log_fuzzy_rdd_bin)
print(log_bw_ik_fuzzy_bin)


#Nonparametric Local Linear RDD Regression
log_nonpara_fuz_bin <- rdd_reg_np(rdd_object = log_fuzzy_rdd_bin, bw = log_bw_ik_fuzzy_bin)
print(log_nonpara_fuz_bin)


#Parametric Probit RDD Regression
log_para_fuz_bin <- rdd_gen_reg(rdd_object = log_fuzzy_rdd_bin, fun = glm, bw = log_bw_ik_fuzzy_bin,
                        family = binomial(link = 'probit'),
                        slope = 'separate', order = 1)
print(log_para_fuz_bin)


# Regression Sensitivity Tests

  ## LATE vs bw (check sensitivity of estimate to different bandwidths)

    ### Nonparametric Fit
plotSensi(log_nonpara_fuz_bin, output = 'ggplot') +
  xlim(log_bw_ik_fuzzy_bin - 0.1, log_bw_ik_fuzzy_bin + 0.1) +
  geom_hline(yintercept = 0, color = 'black', linetype = 'dashed') +
  labs(x = 'Bandwidth', y = 'LATE',
  title = 'Local Average Treatment Effect (LATE) vs Bandwidth') +
  theme_bw()

    ### Parametric Fit
plotSensi(log_para_fuz_bin, output = 'ggplot') +
  xlim(log_bw_ik_fuzzy_bin - 0.1, log_bw_ik_fuzzy_bin + 0.1) +
  geom_hline(yintercept = 0, color = 'black', linetype = 'dashed') +
  labs(x = 'Bandwidth', y = 'LATE',
  title = 'Local Average Treatment Effect (LATE) vs Bandwidth') +
  theme_bw()

  ## Placebo Test (estimate RDD effect based on fake cutpoints)

    ### Nonparametric Fit
plotPlacebo(log_nonpara_fuz_bin)

    ### Parametric Fit
plotPlacebo(log_para_fuz_bin)
```